---
title: "Overview of Data Sets Included in the Meta-Analysis"
author: "MPT Reanalysis Project (code and text current document: Henrik Singmann)"
date: "Results from: `r Sys.Date()`"
output: html_document
---

<style>
  .main-container {
    max-width: 1300px !important;
  }
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
options(width = 150)
```

```{r, include=FALSE}
library(checkpoint)
checkpoint("2020-04-25")
library("MPTmultiverse")
library("tidyverse")
tmpe <- new.env()
source("../fun_prep.R", local = tmpe)
check_set <- get(x = "check_set",envir = tmpe)
check_core_pars <- get(x = "check_core_pars",envir = tmpe)
load("../combined_results.RData")
source("../fun_analysis.R")

## check that datasets are unique:
dm %>% 
  filter(inter == "Comp MLE") %>% 
  group_by(dataset) %>% 
  tally() %>% 
  {stopifnot(all(.$n == 1))}

```

## Models

The results include 9 different models (some of which with additional submodels):

- `2htsm`: 2-high threshold source memory model
- `c2ht`: confidence-rating 2-high threshold memory model
- `pc`: pair-clustering model
- `pd`: process-dissociation
- `pm`: prospective memory model
- `hb`: hindsight-bias model
- `rm`: r-model
- `real`: real model (IAT)
- `quad`: quad model (IAT)

## Participants and Studies

```{r}
n_participants <- dm %>%
  unnest(est_indiv) %>%
  group_by(model, dataset, orig_condition, inter, model2, id) %>%
  summarise(parameter = first(parameter)) %>%
  tally(name = "n_participant")

n_participants %>%
  group_by(model, dataset, orig_condition, model2) %>%
  summarise(check = all(n_participant == first(n_participant))) %>%
  {all(.$check)}  %>% 
  stopifnot()

# n_participants %>%
#   group_by(model, dataset, orig_condition, model2) %>%
#   summarise(check = all(n_participant == first(n_participant))) %>%
#   filter(!check)

n_participants <- n_participants %>%
  group_by(model, dataset, orig_condition, model2) %>%
  summarise(n_participant = first(n_participant)) %>%
  ungroup()
```


The following table gives an overview of the number of conditions (`n_within_between` is the number of conditions that each provide at least one parameter per model that otherwise would not be unique given the base-model equations, this includes both within-subjects and between-conditions; `n_between` is the number of between-subjects conditions), number of participants (`par`), and number of data sets (`n_study`). The final table shows the overall results.

```{r}
n_wb <- dm %>% 
  filter(inter == "Comp MLE") %>% 
  unnest(est_group) %>% 
  group_by(model, condition, dataset) %>% 
  summarise(parameter = first(parameter)) %>% 
  group_by(model) %>% 
  tally(name = "n_within_between")

n_study <- dm %>% 
  filter(inter == "Comp MLE") %>% 
  unnest(est_group) %>% 
  group_by(model, dataset) %>% 
  summarise(parameter = first(parameter)) %>% 
  group_by(model) %>% 
  tally(name = "n_study")

n_tab <- n_participants %>% 
  group_by(model) %>% 
  summarise(n_between = n(), 
            par = sum(n_participant)) %>% 
  left_join(n_study, by = "model") %>% 
  left_join(n_wb, by = "model") %>% 
  select(model, par, n_within_between, n_between, n_study)

n_tab
n_tab %>% 
  summarise_if(is.numeric, sum)
```

We can also make this table by submodel.

```{r}
n_wb <- dm %>% 
  filter(inter == "Comp MLE") %>% 
  unnest(est_group) %>% 
  group_by(model2, condition, dataset) %>% 
  summarise(parameter = first(parameter)) %>% 
  group_by(model2) %>% 
  tally(name = "n_within_between")

n_study <- dm %>% 
  filter(inter == "Comp MLE") %>% 
  unnest(est_group) %>% 
  group_by(model2, dataset) %>% 
  summarise(parameter = first(parameter)) %>% 
  group_by(model2) %>% 
  tally(name = "n_study")

n_tab <- n_participants %>% 
  group_by(model2) %>% 
  summarise(n_between = n(), 
            par = sum(n_participant)) %>% 
  left_join(n_study, by = "model2") %>% 
  left_join(n_wb, by = "model2") %>% 
  select(model2, par, n_within_between, n_between, n_study)

n_tab
n_tab %>% 
  summarise_if(is.numeric, sum)
```


## Methods

The following table gives the proportion of data sets for which a given method (in columns) produced usable results (i.e., also considering our convergence criteria). This first table is separated by models.

```{r}
dm$use <- NA
for (i in seq_len(nrow(dm))) {
  dm[i, "use"] <- check_fit(dm[i,])
}
#prop.table(table(dm$use, useNA = "ifany"))

meth_over <- dm %>% 
  filter(use) %>% 
  select(model, dataset, inter) %>% 
  reshape2::dcast(model + dataset ~ inter, fun.aggregate = length, 
                  value.var = "inter") %>% 
  as_tibble

meth_over %>% 
  group_by(model) %>% 
  summarise_if(is.numeric, .funs = mean)

#levels(dm$inter)

exclude_methods <- c("LC PP") ## could be a value of inter

results <- dm %>% 
  filter(use) %>% 
  filter(!(inter %in% exclude_methods)) %>% 
  droplevels
```

One thing that is clear is that the latent class approach (`LC PP`) is missing in the vast majority of cases. 

We can also look at this across all models.

```{r}
meth_over %>% 
  #group_by(model) %>% 
  summarise_if(is.numeric, .funs = mean)
```


## Methods per Data Set

The following tables, which are separated by model, provide an overview of whether each method is usable (`TRUE`), misses our convergence criteria (`FALSE`), or is missing (`NA`).

```{r}
dm %>% 
  select(model, dataset, inter, use) %>% 
  reshape2::dcast(model + dataset ~ inter,  
                  value.var = "use") %>% 
  as_tibble %>% 
  group_split(model) %>% 
  walk(print, n = Inf)
```

## Core Parameters Per Model

The following gives an overview of the core and (if present) non-core parameters for each model.

```{r}
dm %>% 
  group_split(model) %>% 
  walk(~{
    cat(paste(.$model[1]), "\n")
    check_core_pars(.)
    cat("\n")
    })
```

## Pairwise Plots of Core Parameters

We plot the core parameters for each condition that are usable in the following plot.

```{r, fig.width=12, fig.height=12, warning=FALSE}
results <- dm %>% 
  filter(use) %>% 
  #filter(!(inter %in% exclude_methods)) %>% 
  droplevels

all_pars <- unnest(results, est_group) %>% 
  filter(core) %>% 
  droplevels()

pairs <- combn(sort(levels(all_pars$inter)), 2)
pairs <- combn(levels(all_pars$inter), 2)

all_pars_l <- vector("list", ncol(pairs))

for (i in seq_len(ncol(pairs))) {
  tmp_dat <- all_pars %>% 
    filter(inter %in% pairs[,i]) %>% 
    mutate(inter = factor(inter, 
                           levels = unique(as.character(unlist(pairs[,i]))))) %>% 
    select(model, model_type, dataset, condition, parameter, est, inter) %>% 
    spread(key = inter, value = est)
  colnames(tmp_dat)[(ncol(tmp_dat)-1):ncol(tmp_dat)] <- c("x", "y")
  tmp_dat$cond_x <- pairs[1,i]
  tmp_dat$cond_y <- pairs[2,i]
  all_pars_l[[i]] <- tmp_dat 
}
all_pars2 <- bind_rows(all_pars_l)
#all_pars2 <- left_join(all_pars2, trials)
all_pars2 <- all_pars2 %>% 
  mutate(
    cond_x = factor(cond_x, levels = 
                      levels(all_pars$inter)[unique(all_pars2$cond_x) %in% levels(all_pars$inter)]),
    cond_y = factor(cond_y, levels = 
                      levels(all_pars$inter)[unique(all_pars2$cond_y) %in% levels(all_pars$inter)])
    )

all_pars3 <- all_pars2 %>%
  # filter(restriction == "rrest", parameter %in% c("Do", "Dn", "g")) %>%
  # mutate(parameter = factor(parameter,
  #                           levels = c("Do", "Dn", "g"))) %>%
  mutate(cond_x2 = cond_y,
         cond_y2 = cond_x)

pars_plot <- all_pars3 

pars_plot %>% 
  ggplot(aes(x = x, y = y)) +
  geom_abline(slope = 1, intercept = 0) +
  geom_point(alpha = 0.2) + #aes(size = trials)
  facet_grid(cond_x2~ cond_y2, switch = "both", as.table = FALSE) +
  # geom_text(data=plot_text,
  #           aes(x = 0.2, y = 0.9, label=ccc), 
  #           parse = TRUE, inherit.aes=FALSE, size = 5) +
  coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
  scale_size(range = c(0.5, 2.5)) +
  labs(x = "", y = "") +
  theme(legend.position = "none")

```


## All Pairwise Plots

We can also plot all pairwise plots (instead of only the upper half of the pairs-matrix) and overlay each plot with a GAM.

```{r, fig.width=12, fig.height=12, warning=FALSE}

pairs <- expand.grid(cond_x = sort(levels(all_pars$inter)), 
                     cond_y = sort(levels(all_pars$inter)))



all_pars_l2 <- vector("list", nrow(pairs))

for (i in seq_len(nrow(pairs))) {
  tmp_dat <- all_pars %>% 
    filter(core) %>% 
    filter(inter %in% unlist(pairs[i,])) %>% 
    mutate(inter2 = factor(inter, 
                           levels = unique(as.character(unlist(pairs[i,]))))) %>% 
    select(model, model_type, dataset, condition, parameter, est, inter2) %>% 
    spread(key = inter2, value = est)
  if ( (colnames(tmp_dat)[ncol(tmp_dat)-1]) == "parameter" ) {
    tmp_dat$y <- tmp_dat[[ncol(tmp_dat)]]
  }
  colnames(tmp_dat)[(ncol(tmp_dat)-1):ncol(tmp_dat)] <- c("x", "y")
  tmp_dat$cond_x <- pairs[i, 1]
  tmp_dat$cond_y <- pairs[i, 2]
  all_pars_l2[[i]] <- tmp_dat 
}
all_pars_a2 <- bind_rows(all_pars_l2)
#all_pars2 <- left_join(all_pars2, trials)
all_pars_a2 <- all_pars_a2 %>% 
  mutate(
    cond_x = factor(cond_x, levels = 
                      levels(results$inter)),
    cond_y = factor(cond_y, levels = 
                      levels(results$inter))
    )
all_pars_a3 <- all_pars_a2 %>%
  # filter(restriction == "rrest", parameter %in% c("Do", "Dn", "g")) %>%
  # mutate(parameter = factor(parameter,
  #                           levels = c("Do", "Dn", "g"))) %>%
  mutate(cond_x2 = cond_y,
         cond_y2 = cond_x) %>% 
  filter(!(str_detect(dataset, "Smith et al 2014")))

all_pars_a3 %>% 
  filter(!(model %in% "pm")) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_abline(slope = 1, intercept = 0) +
  geom_point(alpha = 0.2) + #aes(size = trials)
  facet_grid(cond_x2~ cond_y2, switch = "both", as.table = FALSE) +
  coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
  scale_size(range = c(0.5, 2.5)) +
  geom_smooth() +
  labs(x = "", y = "") +
  theme(legend.position = "none")
```

