---
title: "Multivariate Relationships with Absolute Deviation (w/o PC)"
author: "MPT Reanalysis Project (code and text current document: Henrik Singmann)"
date: "Results from: `r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
---

<style>
  .main-container {
    max-width: 1200px !important;
  }
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
options(width = 125)
options(pillar.sigfig = 2)
library("afex")
library("glinternet")
library("RAMP")
library("MuMIn")
library("tidyverse")
theme_set(theme_bw(base_size = 15) + 
            theme(legend.position="bottom"))
source("fun_multivariate_rmse.R")
INCLUDE_GAM <- TRUE
options('na.action' = NULL)   ## for MuMIn::dredge
```

```{r load, include=FALSE}
load("../all_pairs_core.RData")
all_pairs <- all_pairs %>% 
  filter(model != "pc", parameter != "rm:g") %>% 
  droplevels()
str(all_pairs)
all_pairs <- all_pairs %>% 
  filter(cond_x != "No Bayes", cond_y != "No Bayes") %>% 
  mutate(rel_weight = (rel_par_weight_x + rel_par_weight_y)/2,
         rel_n = (rel_n_x + rel_n_y) / 2,
         y_c = y - 0.5) %>% 
  mutate(se_x_w = if_else(se_x > 0.25, 0.25, se_x),
         se_y_w = if_else(se_y > 0.25, 0.25, se_y),
         rel_n_w = if_else(rel_n > 15000, 15000, rel_n)) %>%
  mutate(se_c = (se_x_w + se_y_w)/2) %>% 
    mutate(cond_x2 = cond_y,
         cond_y2 = cond_x) 

rel_vars <- c("se_x_w", "se_y_w", "fungi_max", "rel_weight", "rel_n_w")
other_vars <- c("y", "sd_emp_inv", "rho_med", "p_hetero", "p_fit_x")

rel_vars2 <- c("se_x_w", "se_y_w", "fungi_max", 
                "log(rel_weight)", "log(rel_n_w)")

rel_vars3 <- c("se_c", "fungi_max", 
                "log(rel_weight)", "log(rel_n_w)")

all_vars <- c(rel_vars3, "poly(y_c, 2, raw = TRUE)", "sd_emp_inv", "rho_med", 
              "log1p(p_hetero)", "log1p(p_fit_x)")
all_vars2 <- c(rel_vars3, "y_c", "sd_emp_inv", "rho_med", 
              "log1p(p_hetero)", "log1p(p_fit_x)")

form_main_sel <- paste0("abs_dev ~ ", paste(rel_vars3, collapse = " + "))

form_main <- paste0("abs_dev ~ ", paste(all_vars, collapse = " + "))
form_main2 <- paste0("abs_dev ~ ", paste(all_vars2, collapse = " + "))

form_inter2 <- paste0("abs_dev ~ (", paste(all_vars, collapse = " + "), ")^2")
form_inter2_sel <- paste0("abs_dev ~ (", paste(rel_vars3, collapse = " + "), ")^2")

form_inter <- paste0("abs_dev ~ ", paste(all_vars, collapse = " * "))

form_selection <- paste0("abs_dev ~ ", 
                         paste(c("se_c", "poly(y_c, 2, raw = TRUE)", "log(rel_weight)"), 
                               collapse = " + "))

all_pairs <- all_pairs %>% 
  mutate(filtervar = create_filter_from_formula(form_main)) %>% 
  filter(filtervar)

```


# Overview

This document provides an overview of the multivariate relationships of all moderators with the absolute parameter deviation.  As in the analysis of the univariate relationships we focus on two reference methods, the complete pooling MLE method and the latent-trait partial pooling method. 

In all the analyses reported here, we remove the no pooling Bayes method, as it behaved markedly different from all other methods.

```{r}
sel_methods <- c("Comp MLE", "No asy", "Beta PP", "Trait PP")
targ_cmle <- all_pairs %>% 
  filter(cond_y == "Comp MLE") %>% 
  filter(cond_x != "Comp MLE")
targ_lpp <- all_pairs %>% 
  filter(cond_y == "Trait PP") %>% 
  filter(cond_x != "Trait PP")

targ_both <- bind_rows(targ_cmle, targ_lpp) %>% 
  #filter(cond_x %in% sel_methods) %>% 
  droplevels %>% 
  mutate(cond_label = factor(paste("DV:", cond_y), 
                             levels = c("DV: Comp MLE", "DV: Trait PP"))) %>% 
  mutate(cond_iv_label = factor(paste("IV:", cond_x), levels = 
                                  paste(paste("IV:", levels(cond_x)))))
```

```{r}
ylab <- "Abs. deviation (Comp MLE)"
```

# Correlations and Multicollinearity (all pairs)

When looking at the multivariate relationships, we need to consider the degree of multicollinearity that could be present in the data. The following plot shows the distribution of correlations across all pairs of moderators in the data across each pair of one of the reference methods with each other method. More specifically, each data point underlying the depiction in each row of the figure is the correlation for these two moderators for one pair of methods where in each case at least one of the methods in each pair is one of the two reference methods. The figure then depicts the median of these distribution as a solid point and the error bars depict the minimum and the maximum.

This figure shows that for several of the pairs there is substantial correlation between .25 and .5, but for only one pair is the correlation consistently above .5, with the median just above .75. This is for the two standard errors. Therefore, in the following we combine both standard error estimates into one average.


```{r, include=FALSE}
cors_cmle <- targ_cmle %>% 
  group_by(cond_x)  %>% 
  mutate(rel_weight = log(rel_weight),
         rel_n = log(rel_n),
         p_hetero = log1p(p_hetero),
         p_fit_x = log1p(p_fit_x)) %>% 
  select(c(rel_vars, other_vars)) %>%
  nest() %>% 
  summarise(cor = map(data, 
                      ~as_tibble(cor(., use = "na.or"), rownames = "par1"))) %>% 
  mutate(cor = map(cor, ~pivot_longer(., -par1, names_to = "par2", values_to = "cor"))) %>% 
  unnest(cor) %>% 
  filter(par1 != par2) %>% 
  pivot_wider(c(par1, par2), names_from = "cond_x", values_from = "cor") 

cors_lpp <- targ_lpp %>% 
  group_by(cond_x)  %>% 
  mutate(rel_weight = log(rel_weight),
         rel_n = log(rel_n),
         p_hetero = log1p(p_hetero),
         p_fit_x = log1p(p_fit_x)) %>% 
  select(c(rel_vars, other_vars)) %>%
  nest() %>% 
  summarise(cor = map(data, 
                      ~as_tibble(cor(., use = "na.or"), rownames = "par1"))) %>% 
  mutate(cor = map(cor, ~pivot_longer(., -par1, names_to = "par2", values_to = "cor"))) %>% 
  unnest(cor) %>% 
  filter(par1 != par2) %>% 
  pivot_wider(c(par1, par2), names_from = "cond_x", values_from = "cor") 

cors_both <- left_join(cors_cmle, cors_lpp, 
                       by = c("par1", "par2"), suffix = c(".cmle", ".lpp")) %>% 
  filter(par2 != "se_x", par1 != "rel_n") #%>% 
  #select(par1:`Comp Bayes.cmle`) 
## filter out all repeating columns
cors_both$corr <- NA_character_
for (i in 1:nrow(cors_both)) {
  tmp <- sort(c(cors_both$par1[i], cors_both$par2[i]))
  cors_both$corr[i] <- paste(tmp, collapse = "-")
}
uncorrs <- cors_both$corr %>% unique
cors_both <- cors_both %>% 
  slice(map_dbl(uncorrs, ~which(. == cors_both$corr)[1])) %>% 
  mutate(corr = paste(par1, "-", par2)) %>% 
  mutate(corr = factor(corr, levels = rev(unique(corr))))

cors_agg <- cors_both %>% 
  pivot_longer(cols = -c(par1, par2, corr)) %>% 
  group_by(corr) %>% 
  summarise(min = min(value), 
            max = max(value),
            median = median(value),
            mean = mean(value),
            sd = sd(value)) 
```


```{r, fig.width=6, fig.height=8}
ggplot(cors_agg, aes(x = median, y = corr)) +
  geom_errorbarh(aes(xmin = min, xmax = max), height = 0) +
  geom_point() + 
  coord_cartesian(x = c(-1,1)) +
   theme(panel.grid.major.x = element_line())

```

The following table lists some summary statistics of the correlation distribution ordered by largest absolute minimum correlation:

```{r}
cors_agg %>% 
  arrange(desc(abs(min)))



```

The following table lists the same correlation distribution summary statistics ordered by largest absolute maximum correlation:

```{r}
cors_agg %>% 
  arrange(desc(abs(max)))
```

The following table lists the same correlation distribution summary statistics ordered by largest absolute median:

```{r}
cors_agg %>% 
  arrange(desc(abs(median))) %>% 
  print(n = 20)
```

# Correlations and Multicollinearity (selected pairs)

Same as above, but only looking at the selected method pairs reported in the paper.

This figure shows that for several of the pairs there is substantial correlation between .25 and .5, but for only one pair is the correlation consistently above .5, with the median at .75. This is for the two standard errors. Therefore, in the following we combine both standard error estimates into one average.

```{r, include=FALSE}

cors_cmle <- targ_cmle %>% 
  filter(cond_x %in% sel_methods) %>% 
  group_by(cond_x)  %>% 
  mutate(rel_weight = log(rel_weight),
         rel_n = log(rel_n),
         p_hetero = log1p(p_hetero),
         p_fit_x = log1p(p_fit_x)) %>% 
  select(c(rel_vars, other_vars)) %>%
  nest() %>% 
  summarise(cor = map(data, 
                      ~as_tibble(cor(., use = "na.or"), rownames = "par1"))) %>% 
  mutate(cor = map(cor, ~pivot_longer(., -par1, names_to = "par2", values_to = "cor"))) %>% 
  unnest(cor) %>% 
  filter(par1 != par2) %>% 
  pivot_wider(c(par1, par2), names_from = "cond_x", values_from = "cor") 

cors_lpp <- targ_lpp %>%
  filter(cond_x %in% sel_methods) %>% 
  group_by(cond_x)  %>% 
  mutate(rel_weight = log(rel_weight),
         rel_n = log(rel_n),
         p_hetero = log1p(p_hetero),
         p_fit_x = log1p(p_fit_x)) %>% 
  select(c(rel_vars, other_vars)) %>%
  nest() %>% 
  summarise(cor = map(data, 
                      ~as_tibble(cor(., use = "na.or"), rownames = "par1"))) %>% 
  mutate(cor = map(cor, ~pivot_longer(., -par1, names_to = "par2", values_to = "cor"))) %>% 
  unnest(cor) %>% 
  filter(par1 != par2) %>% 
  pivot_wider(c(par1, par2), names_from = "cond_x", values_from = "cor") 

cors_both <- left_join(cors_cmle, cors_lpp, 
                       by = c("par1", "par2"), suffix = c(".cmle", ".lpp")) %>% 
  filter(par2 != "se_x", par1 != "rel_n") #%>% 
  #select(par1:`Comp Bayes.cmle`) 
## filter out all repeating columns
cors_both$corr <- NA_character_
for (i in 1:nrow(cors_both)) {
  tmp <- sort(c(cors_both$par1[i], cors_both$par2[i]))
  cors_both$corr[i] <- paste(tmp, collapse = "-")
}
uncorrs <- cors_both$corr %>% unique
cors_both <- cors_both %>% 
  slice(map_dbl(uncorrs, ~which(. == cors_both$corr)[1])) %>% 
  mutate(corr = paste(par1, "-", par2)) %>% 
  mutate(corr = factor(corr, levels = rev(unique(corr))))

cors_agg <- cors_both %>% 
  pivot_longer(cols = -c(par1, par2, corr)) %>% 
  group_by(corr) %>% 
  summarise(min = min(value), 
            max = max(value),
            median = median(value),
            mean = mean(value),
            sd = sd(value)) 
```


```{r, fig.width=6, fig.height=8}

ggplot(cors_agg, aes(x = median, y = corr)) +
  geom_errorbarh(aes(xmin = min, xmax = max), height = 0) +
  geom_point() + 
  coord_cartesian(x = c(-1,1)) +
   theme(panel.grid.major.x = element_line())

```

The following table lists the correlation ordered by largest absolute minimum:

```{r}
cors_agg %>% 
  arrange(desc(abs(min)))



```

The following table lists the correlation ordered by largest absolute maximum:

```{r}
cors_agg %>% 
  arrange(desc(abs(max)))
```

The following table lists the correlation ordered by largest absolute median:

```{r}
cors_agg %>% 
  arrange(desc(abs(median))) %>% 
  print(n = 20)
```


# Multiple Regression

We then consider multiple regression models. 

```{r, results='hide', include=FALSE}
all_lm <- targ_both %>% 
  group_by(cond_label, cond_iv_label)  %>% 
  summarise(
    mean = list(lm(abs_dev ~ 1)),
    parameter = list(lm(abs_dev ~ parameter)),
    mse_both = list(lm(abs_dev ~ se_x_w + se_y_w)),
    mse_c = list(lm(abs_dev ~ se_c)),
    main = list(lm(formula(form_main))), 
    main_good = list(lm(formula(form_main_sel))), 
    #main_sel = list(lm(formula(form_selection))), 
    #main_sel_beta = list(lm_scale(formula(form_main_sel))), 
    inter_2 = list(lm(formula(form_inter2))),
    inter_2_good = list(lm(formula(form_inter2_sel))),
    se_y_fungi = list(lm(abs_dev ~ se_c + poly(y_c, 2, raw = TRUE) + fungi_max)),
    se_y = list(lm(abs_dev ~ se_c + poly(y_c, 2, raw = TRUE)))
    #inter_all = list(lm(formula(form_inter)))
  ) %>% 
  ungroup
all_lm2 <- targ_both %>% 
  group_by(cond_label, cond_iv_label) %>% 
  nest() %>% 
  mutate(
    # best2 = map(data, best_x, formula = form_main, fixed = ~se_c, x = 2),
    # best3 = map(data, best_x, formula = form_main, fixed = ~se_c, x = 3)
    best2 = map(data, best_x, formula = form_main, fixed = NULL, x = 2),
    #best2_lin = map(data, best_x, formula = form_main2, fixed = NULL, x = 2),
    best3 = map(data, best_x, formula = form_main, fixed = NULL, x = 3)
    #best3_lin = map(data, best_x, formula = form_main2, fixed = NULL, x = 3)
  ) %>% 
  ungroup
all_lm <- left_join(all_lm, select(all_lm2, -data))
```


Here, we first consider several model variants (in addition to the baseline model, `mean`, and the `parameter` model) of the nine moderators (there are ten moderators initially, and because we combine both standard error estimates we end up with nine). As further possible models we also consider a model with both separate standard errors, `mse_both` (entered as main effects) and one with only the combined standard error (`mse_c`). Also, for the estimate itself (`y`) we consider a linear and quadratic trend which is why we add two coefficients for this moderator in each model. Also, we always use the same transformation as presented in the figures in the paper (e.g., log for relative information). The following additional models are included:


- `main`: Main effects only (i.e., all effects are additive)
- `main_good`: Main effects of the four "good" moderators (SE, parameter trade-offs, relative information, and relative N).
- `inter_2`: main effects and second order interactions of all moderators.
- `inter_2_godd`: main effects and second order interactions of the four "good" moderators.
- `best2` best model with two moderators as main effects (one of which is the combined standard error)
- `best3` best model with three moderators as main effects (one of which is the combined standard error)
- `se_y_fungi`: standard error, value of the estimate, and parameter trade-off
- `se_y`: standard error and value of the estimate

These models have the following numbers of parameters. 

```{r}
all_lm %>% 
  mutate(across(where(is.list), ~map_dbl(.x, function(x) length(coef(x)))))
```

The following table shows the resulting RMSE for all models. 

```{r}
all_lm %>% 
  mutate(across(where(is.list), ~map_dbl(.x, sigma)))
```

We can also reduce this table to only the comparison methods selected in the paper:

```{r}
all_lm %>% 
  mutate(across(where(is.list), ~map_dbl(.x, sigma))) %>% 
  slice(2, 5, 7, 8, 10, 13) %>% 
  select(-mean)
```

The results show that the model with all `main` effects usually provides an account that is very similar to the `parameter` model. The model only containing the "good" moderators fares slightly worse but not much. Even including interaction does not bring too much, akthough including all adds many parameters.

The following table shows the additional variable in the model with the best two moderators and the two additional predictors in the model with the best three moderators.

```{r}

# all.vars(all_lm2$best2[[1]]$call)[2]
# all.vars(all_lm2$best2[[1]]$call)[2]

all_lm2 <- all_lm2 %>% 
  mutate(
    b2_1 = map_chr(best2, ~all.vars(.$call[[2]])[3]),
    b2_2 = map_chr(best2, ~all.vars(.$call[[2]])[2]),
    #b2l_1 = map_chr(best2_lin, ~all.vars(.$call[[2]])[3]),
    #b2l_2 = map_chr(best2_lin, ~all.vars(.$call[[2]])[2]),
    b3_1 = map_chr(best3, ~all.vars(.$call[[2]])[4]),
    b3_2 = map_chr(best3, ~all.vars(.$call[[2]])[3]),
    b3_3 = map_chr(best3, ~all.vars(.$call[[2]])[2])
    # b3l_1 = map_chr(best3_lin, ~all.vars(.$call[[2]])[4]),
    # b3l_2 = map_chr(best3_lin, ~all.vars(.$call[[2]])[3]),
    # b3l_3 = map_chr(best3_lin, ~all.vars(.$call[[2]])[2])
  )

all_lm2 %>% 
  select(cond_label, cond_iv_label, b2_1:b3_3) %>% 
  slice(2, 5, 7, 8, 10, 13)

```

The following plot shows the coeffcicients for the model with SE, value (linear and quadratic) and fungibility.

```{r, fig.width=7.5, fig.height=5}
best3_pars <- all_lm %>% 
  slice(2, 5, 7, 8, 10, 13) %>% 
  group_by(cond_label, cond_iv_label) %>%
  #summarise(map_df(main_sel, ~broom::tidy(.))) %>% 
  summarise(map_df(se_y_fungi, ~broom::tidy(.))) %>% 
  ungroup() %>% 
  mutate(Methods = cond_label:cond_iv_label)
levels(best3_pars$Methods) <- str_remove(levels(best3_pars$Methods), "DV: ")
levels(best3_pars$Methods) <- str_replace(levels(best3_pars$Methods), 
                                          ":IV: ", " - ")

best3_pars$term <- factor(
  x = best3_pars$term,
  levels = rev(c("(Intercept)", "se_c", "poly(y_c, 2, raw = TRUE)1", 
             "poly(y_c, 2, raw = TRUE)2", "fungi_max")), 
  labels = rev(c("Intercept", "SE", "Value (lin)", "Value (quad)", 
             "Trade-offs"))
    )

# best3_pars %>% 
#   filter(term == "poly(y_c, 2, raw = TRUE)2")

best3_agg <- best3_pars %>% 
  group_by(term) %>% 
  summarise(mean = mean(estimate),
            median = median(estimate))

best3_agg

pmulti <- ggplot(best3_pars, aes(y = term, x = estimate)) +
  geom_vline(xintercept = 0, colour = "darkgrey") +
  geom_point(aes(shape = Methods)) +
  geom_point(data = best3_agg, aes(x = mean, color = "Mean estimate"), shape = 4) +
  # geom_point(data = best3_agg, aes(x = median), color = "blue")
  labs(x = "Multiple regression estimate", y = "Multiple regression coefficient") + 
  scale_color_manual("", values = "red") + 
  theme(legend.position="bottom", legend.box = "vertical")
  #stat_summary(fun.y = mean, fun.ymax = mean, fun.ymin = mean, color = "red")
pmulti
ggsave("../figures_man/multi_estimates_noPC.png", device = "png", 
       width = 20.5, height = 12.5, units = "cm", 
       dpi = 600)
```


```{r}
cors_cmle <- targ_cmle %>% 
  filter(cond_x %in% sel_methods) %>% 
  group_by(cond_x)  %>% 
  mutate(rel_weight = log(rel_weight),
         rel_n = log(rel_n),
         p_hetero = log1p(p_hetero),
         p_fit_x = log1p(p_fit_x),
         y_c_quad = y_c^2) %>% 
  select(se_c, y_c, y_c_quad, fungi_max) %>%
  nest() %>% 
  summarise(cor = map(data, 
                      ~as_tibble(cor(., use = "na.or"), rownames = "par1"))) %>% 
  mutate(cor = map(cor, ~pivot_longer(., -par1, names_to = "par2", values_to = "cor"))) %>% 
  unnest(cor) %>% 
  filter(par1 != par2) %>% 
  pivot_wider(c(par1, par2), names_from = "cond_x", values_from = "cor") 

cors_lpp <- targ_lpp %>%
  filter(cond_x %in% sel_methods) %>% 
  group_by(cond_x)  %>% 
  mutate(rel_weight = log(rel_weight),
         rel_n = log(rel_n),
         p_hetero = log1p(p_hetero),
         p_fit_x = log1p(p_fit_x),
         y_c_quad = y_c^2) %>% 
  select(se_c, y_c, y_c_quad, fungi_max) %>%
  nest() %>% 
  summarise(cor = map(data, 
                      ~as_tibble(cor(., use = "na.or"), rownames = "par1"))) %>% 
  mutate(cor = map(cor, ~pivot_longer(., -par1, names_to = "par2", values_to = "cor"))) %>% 
  unnest(cor) %>% 
  filter(par1 != par2) %>% 
  pivot_wider(c(par1, par2), names_from = "cond_x", values_from = "cor") 

cors_both <- left_join(cors_cmle, cors_lpp, 
                       by = c("par1", "par2"), suffix = c(".cmle", ".lpp")) %>% 
  filter(par2 != "se_c", par1 != "fungi_max") #%>% 
  #select(par1:`Comp Bayes.cmle`) 
## filter out all repeating columns
cors_both$corr <- NA_character_
for (i in 1:nrow(cors_both)) {
  tmp <- sort(c(cors_both$par1[i], cors_both$par2[i]))
  cors_both$corr[i] <- paste(tmp, collapse = "-")
}
uncorrs <- cors_both$corr %>% unique
cors_both <- cors_both %>% 
  slice(map_dbl(uncorrs, ~which(. == cors_both$corr)[1])) %>% 
  mutate(corr = paste(par1, "-", par2)) %>% 
  mutate(corr = factor(corr, levels = rev(unique(corr))))

cors_agg <- cors_both %>% 
  pivot_longer(cols = -c(par1, par2, corr)) %>% 
  group_by(corr) %>% 
  summarise(min = min(value), 
            max = max(value),
            median = median(value),
            mean = mean(value),
            sd = sd(value)) 
```

Overview of correlations in model with three best coefficients:

```{r}
cors_agg
```


```{r, eval=FALSE, echo=FALSE, include=FALSE}
all_lm %>% 
  mutate(across(where(is.list), ~map_dbl(.x, function(x) nrow(x$model))))


summary(all_lm$mse_c[[3]])
summary(all_lm$mse_c[[4]])

nrow(all_lm$main[[1]]$model)

summary(all_lm$main_sel[[1]])
coef(lm.beta::lm.beta(all_lm$main_sel[[1]]))
coef((all_lm$main_sel[[1]]))

all_lm %>% 
  group_by(cond_label, cond_iv_label) %>%
  #summarise(map_df(main_sel, ~broom::tidy(.))) %>% 
  summarise(map_df(main_selected, ~broom::tidy(lm.beta::lm.beta(.)))) %>% 
  ungroup() %>% 
  ggplot(aes(y = term, x = estimate)) +
  geom_vline(xintercept = 0, colour = "darkgrey") +
  geom_point()


all_lm %>% 
  group_by(cond_label, cond_iv_label) %>%
  #summarise(map_df(main_sel, ~broom::tidy(.))) %>% 
  summarise(map_df(main, ~broom::tidy(lm.beta::lm.beta(.)))) %>% 
  ungroup() %>% 
  ggplot(aes(y = term, x = estimate)) +
  geom_vline(xintercept = 0, colour = "darkgrey") +
  geom_point()
```



# RAMP Model selection



```{r}

all_ramp <- targ_both %>% 
  group_by(cond_label, cond_iv_label)  %>% 
  summarise(
    r = list(fit_ramp(form_main2)),
    r_c = list(fit_ramp(form_main2, center = TRUE))
  )
all_ramp <- left_join(all_ramp, select(all_lm2, cond_label:data))
all_ramp <- all_ramp %>% 
  mutate(
    rmse = map2_dbl(r, data, get_rmse_ramp),
    rmsec = map2_dbl(r_c, data, get_rmse_ramp)
  )
all_ramp <- all_ramp %>% 
  mutate(main = map(r_c, ~.$mainInd), 
         inter = map(r_c, ~.$interInd))

```

RAMP results for selected method pairs (`rmsec`) and number of coefficients in RAMP model:

```{r}
all_ramp %>% 
  ungroup %>% 
  mutate(n = 1 + map_dbl(main, length) + map_dbl(inter, length)) %>% 
  slice(2, 5, 7, 8, 10, 13)
```

Inclusion probability of interactions (only selected method pairs):

```{r}
tmp_ramp <- all_ramp %>% 
  ungroup() %>% 
  slice(2, 5, 7, 8, 10, 13)
  
imat <- Reduce(`+`, map(tmp_ramp$inter, produce_interaction_matrix, 
    length = length(all.vars(formula(form_main2))) -1)) / nrow(tmp_ramp)
dimnames(imat) <- list(colnames(tmp_ramp$r[[1]]$X), colnames(tmp_ramp$r[[1]]$X))
round(imat, 2)

```

We can also calculate how many cells appear how often. The first value in the following list is the number of cells that appear in all 6 possible pairs, the second number is the number of cells that appear in five pairs, and so forth. The last number is the number of cells that appear in no pair.

```{r}
imat <- Reduce(`+`, map(tmp_ramp$inter, produce_interaction_matrix, 
    length = length(all.vars(formula(form_main2))) -1))
dimnames(imat) <- list(colnames(tmp_ramp$r[[1]]$X), colnames(tmp_ramp$r[[1]]$X))

sum(imat == 6)
sum(imat == 5)
sum(imat == 4)
sum(imat == 3)
sum(imat == 2)
sum(imat == 1)
sum(imat[upper.tri(imat, diag = TRUE)] == 0)
sum(c(sum(imat == 6), sum(imat == 5), sum(imat == 4), sum(imat == 3), sum(imat == 2), sum(imat == 1), sum(imat[upper.tri(imat, diag = TRUE)] == 0)))
```

Inclusion vector of main effects

```{r}
mevec <- Reduce(`+`, map(tmp_ramp$main, produce_me_vector, 
    length = length(all.vars(formula(form_main2))) -1)) / nrow(tmp_ramp)
names(mevec) <- colnames(tmp_ramp$r_c[[1]]$X)
mevec
```


RAMP results for all method pairs:

```{r}
all_ramp %>% 
  ungroup 
```

Inclusion of interaction for all method pairs:

```{r}
imat <- Reduce(`+`, map(all_ramp$inter, produce_interaction_matrix, 
    length = length(all.vars(formula(form_main2))) -1)) / nrow(all_ramp)
dimnames(imat) <- list(colnames(all_ramp$r[[1]]$X), colnames(all_ramp$r[[1]]$X))
round(imat, 2)
```


