---
title: "Applying Prediction Rule ENsembles"
author: "MPT Reanalysis Project (code and text current document: Henrik Singmann)"
date: "Results from: `r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
---

<style>
  .main-container {
    max-width: 1200px !important;
  }
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
options(width = 120)
library("pre")
library("tidyverse")
theme_set(theme_bw(base_size = 15) + 
            theme(legend.position="bottom", 
                  panel.grid.major.x = element_blank()))
```

```{r load, include=FALSE}
load("../all_pairs_core.RData")
str(all_pairs)
dput(levels(all_pairs$cond_x))
```


# Overview

This document provides an overview of the univariate relationships of all covariates with the absolute parameter deviation.  We separate the relationships by focussing on one method as the target method and then investigating the relationships for each of the remaining methods with this method.



# DV: Absolute Deviation from Complete Pooling MLE Estimate



```{r}
targ_cmle <- all_pairs %>% 
  filter(cond_y == "Comp MLE") %>% 
  filter(cond_x == "Trait PP") %>% 
  #as.data.frame() %>% 
  select(abs_dev, x, y, 
         se_x, se_y, 
         log1p_hetero, sd_emp_inv, 
         rho_med, fungi_max) %>% 
  na.omit

targ_cmle2 <- all_pairs %>% 
  mutate(is_small = factor(abs_dev < 0.05, 
                           levels = c(TRUE, FALSE))) %>% 
  filter(cond_y == "Comp MLE") %>% 
  filter(cond_x == "Trait PP") %>% 
  #as.data.frame() %>% 
  select(is_small, 
         y, #y, 
         se_y, #se_y, 
         log1p_hetero, sd_emp_inv, 
         rho_med, fungi_max) %>% 
  na.omit
```

```{r}
cur_data <- targ_cmle
ylab <- "Abs. deviation (Comp MLE)"
```

```{r}
set.seed(667)
compmle_ens <- pre(abs_dev ~ ., targ_cmle, winsfrac = 0)
compmle_ens
```


```{r}
imps <- importance(compmle_ens, standardize = TRUE, round = 4L)
```

```{r}
plot(compmle_ens, nterms = 6, plot.dim = c(2, 3), standardize = TRUE, 
     cex = 0.7)
```


```{r}
set.seed(667)
compmle_ens2 <- pre(is_small ~ ., targ_cmle2, winsfrac = 0, 
                    family = "binomial")
compmle_ens2
```

```{r}
imps <- importance(compmle_ens2, round = 4L)
```

```{r}
plot(compmle_ens2, nterms = 6, plot.dim = c(2, 3), cex = 0.7)
```

```{r}
singleplot(compmle_ens2, varname = "se_x")
```


```{r, eval=FALSE}
## fails due to RAM limits.
pairplot(compmle_ens2, varnames = c("se_x", "sd_emp_inv"))
```

