---
title: "SAI & EAI analysis"
author: "MPT Reanalysis Project (code and text current document: Henrik Singmann)"
date: "Results from: `r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
---

<style>
  .main-container {
    max-width: 1200px !important;
  }
</style>


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
options(width = 120)
library("afex")
library("tidyverse")
theme_set(theme_bw(base_size = 15) + 
            theme(legend.position="bottom"))
source("../fun_analysis_paper.R")
source("fun_eai.R")
```

```{r load, include=FALSE}
load("../all_pairs_core.RData")
str(all_pairs)
levels(all_pairs$cond_x) <- new_method_labels(levels(all_pairs$cond_x))
levels(all_pairs$cond_y) <- new_method_labels(levels(all_pairs$cond_y))
all_pairs <- all_pairs %>% 
    mutate(cond_x2 = cond_y,
         cond_y2 = cond_x) %>% 
    mutate(rel_weight = (rel_par_weight_x + rel_par_weight_y)/2,
         rel_n = (rel_n_x + rel_n_y) / 2) %>% 
    mutate(se_x_w = if_else(se_x > 0.25, 0.25, se_x),
         se_y_w = if_else(se_y > 0.25, 0.25, se_y),
         rel_n_w = if_else(rel_n > 15000, 15000, rel_n)) %>% 
  mutate(prop_ns = rowMeans(cbind(prop_ns_nopb, prop_ns_nonpb, prop_ns_noasy, prop_ns_trait), na.rm = TRUE)) %>% 
  mutate(se_c = (se_x_w + se_y_w)/2) %>% 
  mutate(SAI = factor(if_else(model == "pc", "Not SAI", "SAI"), 
                      levels = c("SAI", "Not SAI"))) %>% 
  filter(parameter != "rm:g") %>% 
  mutate(cond_label = factor(paste("R:", cond_y), 
                             levels = c("R: CP-MLE", "R: PP-LT-C"))) %>% 
  mutate(cond_iv_label = factor(paste("C:", cond_x), levels = 
                                  paste(paste("C:", levels(cond_x))))) %>% 
  mutate(z_abs_dev = abs_dev/se_c)
```

```{r PARAMETERS}

CUT_WIDTH_RHO <- 0.05
CUT_WIDTH_SE <- 0.025

MIN_REL_SE <- 0.025
MIN_REL_RHO <- 0.1

```


# Structural Aggregation Invariance (SAI)

If we compare the absolute deviation across method pairs and whether or not SAI holds for a model, the following plot shows that for models for which SAI does not hold (i.e., the pair clustering model) the absolute deviation is on average larger. The red points is the mean in each plot. Consequently, all following analyses are based on the data excluding the non SAI (i.e., pair clustering) model.

```{r, fig.width=11.4, fig.height=11, message=FALSE, eval=TRUE}
all_pairs %>% 
  ggplot(aes(x = SAI, y = abs_dev)) +
  geom_boxplot() +
  stat_summary(color = "red") +
  facet_grid(cond_x2~ cond_y2, switch = "y", as.table = TRUE)
```

```{r}
all_pairs <- all_pairs %>% 
  filter(model != "pc")
```


# Empirical Aggregation Invariance (EAI)

## Reference Method: CP-MLE

```{r}
targ_cmle <- all_pairs %>% 
  filter(cond_y == "CP-MLE") %>% 
  filter(cond_x != "CP-MLE")
```

```{r}
cur_data <- targ_cmle
ylab <- "Abs. deviation (CP-MLE)"
theme_set(theme_bw(base_size = 15) + 
            theme(legend.position="right"))
```

```{r, fig.width=18, fig.height=5, message=FALSE, eval=FALSE}
make_emp_biv_plot(cur_data, 
                  rhos_max, "rel. correlations (max)",
                  se_y, "SE (reference method)")

make_emp_biv_plot(cur_data, 
                  rhos_max, "rel. correlations (max)",
                  se_x, "SE (comparison method)")

make_emp_biv_plot(cur_data, 
                  rhos_max, "rel. correlations (max)",
                  se_c, "SE (combined)")

make_emp_biv_plot(cur_data, 
                  rhos_mean, "rel. correlations (mean)",
                  se_y, "SE (reference method)")

make_emp_biv_plot(cur_data, 
                  rhos_mean, "rel. correlations (mean)",
                  se_x, "SE (comparison method)")

make_emp_biv_plot(cur_data, 
                  rhos_mean, "rel. correlations (mean)",
                  se_x, "SE (combined)")
```

```{r, fig.width=18, fig.height=5, message=FALSE, warning=FALSE}
# make_gam_biv_plot(cur_data, 
#                   rhos_max, "rel. correlations (max)",
#                   se_y, "SE (reference method)")
# 
# make_gam_biv_plot(cur_data, 
#                   rhos_max, "rel. correlations (max)",
#                   se_x, "SE (comparison method)")

make_gam_biv_plot(cur_data, 
                  rhos_max, "rel. correlations (max)",
                  se_c, "SE (combined)") +
  facet_grid(~cond_label+cond_iv_label)

# make_gam_biv_plot(cur_data, 
#                   rhos_mean, "rel. correlations (mean)",
#                   se_y, "SE (reference method)")
# 
# make_gam_biv_plot(cur_data, 
#                   rhos_mean, "rel. correlations (mean)",
#                   se_x, "SE (comparison method)")
# 
# make_gam_biv_plot(cur_data, 
#                   rhos_mean, "rel. correlations (mean)",
#                   se_x, "SE (combined)")
```

### Selected Pairs: SE < .025, Rho < .1

```{r PARAMETERS2}
MIN_REL_SE <- 0.025
MIN_REL_RHO <- 0.1

```

```{r}
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>% 
  select(model2, dataset, parameter, cond_x, cond_y, 
         abs_dev, se_c, rhos_max, x, y, starts_with("prop_ns")) %>% 
  mutate(z_abs_dev = abs_dev/se_c) %>% 
  arrange(desc(z_abs_dev)) %>% 
  slice(1:30) %>% 
  knitr::kable(digits = 3)
```

```{r, fig.width=10, fig.height=3.5, message=FALSE}
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>% 
  mutate(z_abs_dev = abs_dev/se_c) %>% 
  mutate(misfit = ifelse(prop_ns_nonpb 	== 0, "none", "some")) %>% 
  ggplot(aes(x = misfit, y = z_abs_dev)) +
  geom_boxplot() +
  stat_summary(color = "red") +
  facet_grid(~cond_iv_label)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>% 
  mutate(z_abs_dev = abs_dev/se_c) %>% 
  mutate(misfit = ifelse(prop_ns_nonpb 	== 0, "none", "some")) %>% 
  ggplot(aes(x = misfit, y = abs_dev)) +
  geom_boxplot() +
  stat_summary(color = "red") +
  facet_grid(~cond_iv_label)

```

```{r, fig.width=10, fig.height=3, message=FALSE}

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = z_abs_dev)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = z_abs_dev, 
                filter = prop_ns < 0.4)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nopb, y = z_abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nonpb, y = z_abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_noasy, y = z_abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_trait, y = z_abs_dev)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = abs_dev, 
                filter = prop_ns < 0.4)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nopb, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nonpb, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_noasy, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_trait, y = abs_dev)
```

### Selected Pairs: SE < .02, Rho < .05

```{r PARAMETERS3}
MIN_REL_SE <- 0.02
MIN_REL_RHO <- 0.05

```

```{r}
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>% 
  select(model2, dataset, parameter, cond_x, cond_y, 
         abs_dev, se_c, rhos_max, x, y, starts_with("prop_ns")) %>% 
  mutate(z_abs_dev = abs_dev/se_c) %>% 
  arrange(desc(z_abs_dev)) %>% 
  slice(1:30) %>% 
  knitr::kable(digits = 3)
```

```{r, fig.width=10, fig.height=3.5, message=FALSE}
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>% 
  mutate(z_abs_dev = abs_dev/se_c) %>% 
  mutate(misfit = ifelse(prop_ns_nonpb 	== 0, "none", "some")) %>% 
  ggplot(aes(x = misfit, y = z_abs_dev)) +
  geom_boxplot() +
  stat_summary(color = "red") +
  facet_grid(~cond_iv_label)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>% 
  mutate(z_abs_dev = abs_dev/se_c) %>% 
  mutate(misfit = ifelse(prop_ns_nonpb 	== 0, "none", "some")) %>% 
  ggplot(aes(x = misfit, y = abs_dev)) +
  geom_boxplot() +
  stat_summary(color = "red") +
  facet_grid(~cond_iv_label)

```

```{r, fig.width=10, fig.height=3, message=FALSE}

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = z_abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = z_abs_dev, 
                filter = prop_ns < 0.4)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nopb, y = z_abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nonpb, y = z_abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_noasy, y = z_abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_trait, y = z_abs_dev)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = abs_dev, 
                filter = prop_ns < 0.4)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nopb, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nonpb, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_noasy, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_trait, y = abs_dev)
```


## Reference Method:PP-LT-C

```{r}
targ_cmle <- all_pairs %>% 
  filter(cond_y == "PP-LT-C") %>% 
  filter(cond_x != "PP-LT-C")
```

```{r}
cur_data <- targ_cmle
ylab <- "Abs. deviation (PP-LT-C)"
theme_set(theme_bw(base_size = 15) + 
            theme(legend.position="right"))
```

```{r, fig.width=18, fig.height=5, message=FALSE, eval=FALSE}
make_emp_biv_plot(cur_data, 
                  rhos_max, "rel. correlations (max)",
                  se_y, "SE (reference method)")

make_emp_biv_plot(cur_data, 
                  rhos_max, "rel. correlations (max)",
                  se_x, "SE (comparison method)")

make_emp_biv_plot(cur_data, 
                  rhos_max, "rel. correlations (max)",
                  se_c, "SE (combined)")

make_emp_biv_plot(cur_data, 
                  rhos_mean, "rel. correlations (mean)",
                  se_y, "SE (reference method)")

make_emp_biv_plot(cur_data, 
                  rhos_mean, "rel. correlations (mean)",
                  se_x, "SE (comparison method)")

make_emp_biv_plot(cur_data, 
                  rhos_mean, "rel. correlations (mean)",
                  se_x, "SE (combined)")
```

```{r, fig.width=18, fig.height=5, message=FALSE, warning=FALSE}
# make_gam_biv_plot(cur_data, 
#                   rhos_max, "rel. correlations (max)",
#                   se_y, "SE (reference method)")
# 
# make_gam_biv_plot(cur_data, 
#                   rhos_max, "rel. correlations (max)",
#                   se_x, "SE (comparison method)")

make_gam_biv_plot(cur_data, 
                  rhos_max, "rel. correlations (max)",
                  se_c, "SE (combined)") +
  facet_grid(~cond_label+cond_iv_label)

# make_gam_biv_plot(cur_data, 
#                   rhos_mean, "rel. correlations (mean)",
#                   se_y, "SE (reference method)")
# 
# make_gam_biv_plot(cur_data, 
#                   rhos_mean, "rel. correlations (mean)",
#                   se_x, "SE (comparison method)")
# 
# make_gam_biv_plot(cur_data, 
#                   rhos_mean, "rel. correlations (mean)",
#                   se_x, "SE (combined)")
```

### Selected Pairs: SE < .025, Rho < .1

```{r PARAMETERSb1}
MIN_REL_SE <- 0.025
MIN_REL_RHO <- 0.1

```

```{r}
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>% 
  select(model2, dataset, parameter, cond_x, cond_y, 
         abs_dev, se_c, rhos_max, x, y, starts_with("prop_ns")) %>% 
  mutate(z_abs_dev = abs_dev/se_c) %>% 
  arrange(desc(z_abs_dev)) %>% 
  slice(1:30) %>% 
  knitr::kable(digits = 3)
```

```{r, fig.width=10, fig.height=3.5, message=FALSE}
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>% 
  mutate(z_abs_dev = abs_dev/se_c) %>% 
  mutate(misfit = ifelse(prop_ns_nonpb 	== 0, "none", "some")) %>% 
  ggplot(aes(x = misfit, y = z_abs_dev)) +
  geom_boxplot() +
  stat_summary(color = "red") +
  facet_grid(~cond_iv_label)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>% 
  mutate(z_abs_dev = abs_dev/se_c) %>% 
  mutate(misfit = ifelse(prop_ns_nonpb 	== 0, "none", "some")) %>% 
  ggplot(aes(x = misfit, y = abs_dev)) +
  geom_boxplot() +
  stat_summary(color = "red") +
  facet_grid(~cond_iv_label)

```

```{r, fig.width=10, fig.height=3, message=FALSE}

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = z_abs_dev)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = z_abs_dev, 
                filter = prop_ns < 0.4)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nopb, y = z_abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nonpb, y = z_abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_noasy, y = z_abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_trait, y = z_abs_dev)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = abs_dev,
                filter = prop_ns < 0.4)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nopb, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nonpb, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_noasy, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_trait, y = abs_dev)
```

### Selected Pairs: SE < .02, Rho < .05

```{r PARAMETERSb2}
MIN_REL_SE <- 0.02
MIN_REL_RHO <- 0.05

```

```{r}
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>% 
  select(model2, dataset, parameter, cond_x, cond_y, 
         abs_dev, se_c, rhos_max, x, y, starts_with("prop_ns")) %>% 
  mutate(z_abs_dev = abs_dev/se_c) %>% 
  arrange(desc(z_abs_dev)) %>% 
  slice(1:30) %>% 
  knitr::kable(digits = 3)
```

```{r, fig.width=10, fig.height=3.5, message=FALSE}
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>% 
  mutate(z_abs_dev = abs_dev/se_c) %>% 
  mutate(misfit = ifelse(prop_ns_nonpb 	== 0, "none", "some")) %>% 
  ggplot(aes(x = misfit, y = z_abs_dev)) +
  geom_boxplot() +
  stat_summary(color = "red") +
  facet_grid(~cond_iv_label)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>% 
  mutate(z_abs_dev = abs_dev/se_c) %>% 
  mutate(misfit = ifelse(prop_ns_nonpb 	== 0, "none", "some")) %>% 
  ggplot(aes(x = misfit, y = abs_dev)) +
  geom_boxplot() +
  stat_summary(color = "red") +
  facet_grid(~cond_iv_label)

```

```{r, fig.width=10, fig.height=3, message=FALSE}

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = z_abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = z_abs_dev, 
                filter = prop_ns < 0.4)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nopb, y = z_abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nonpb, y = z_abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_noasy, y = z_abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_trait, y = z_abs_dev)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = abs_dev, 
                filter = prop_ns < 0.4)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nopb, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nonpb, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_noasy, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_trait, y = abs_dev)
```

### Selected Pairs: SE < .05, Rho < .1

```{r PARAMETERSb3}
MIN_REL_SE <- 0.05
MIN_REL_RHO <- 0.1

```

```{r}
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>% 
  select(model2, dataset, parameter, cond_x, cond_y, 
         abs_dev, se_c, rhos_max, x, y, starts_with("prop_ns")) %>% 
  mutate(z_abs_dev = abs_dev/se_c) %>% 
  arrange(desc(z_abs_dev)) %>% 
  slice(1:30) %>% 
  knitr::kable(digits = 3)
```

```{r, fig.width=10, fig.height=3.5, message=FALSE}
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>% 
  mutate(z_abs_dev = abs_dev/se_c) %>% 
  mutate(misfit = ifelse(prop_ns 	== 0, "none", "some")) %>% 
  ggplot(aes(x = misfit, y = z_abs_dev)) +
  geom_boxplot() +
  stat_summary(color = "red") +
  facet_grid(~cond_iv_label)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>% 
  mutate(z_abs_dev = abs_dev/se_c) %>% 
  mutate(misfit = ifelse(prop_ns 	== 0, "none", "some")) %>% 
  ggplot(aes(x = misfit, y = abs_dev)) +
  geom_boxplot() +
  stat_summary(color = "red") +
  facet_grid(~cond_iv_label)

```

```{r, fig.width=10, fig.height=3, message=FALSE}

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = z_abs_dev)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = z_abs_dev, 
                filter = prop_ns < 0.4)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nopb, y = z_abs_dev,
                filter = prop_ns_nopb < 0.4)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nonpb, y = z_abs_dev,
                filter = prop_ns_nonpb < 0.1)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_noasy, y = z_abs_dev,
                filter = prop_ns_noasy < 0.5)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_trait, y = z_abs_dev,
                filter = prop_ns_trait < 0.15)

cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns, y = abs_dev,
                filter = prop_ns < 0.4)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nopb, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_nonpb, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_noasy, y = abs_dev)
cur_data %>% 
  filter(rhos_max < MIN_REL_RHO, se_c < MIN_REL_SE) %>%
  make_cor_plot(x = prop_ns_trait, y = abs_dev)
```

